\TheTitle

### 2015-08-12 linvis.tex
Abstract, introduction, and gitk

	With an average of over 900 top-level merges into the Linux kernel per
	release, each containing thousands of commits, maintenance of older
	versions of the kernel becomes nearly impossible. For security,
	performance, and changing hardware, maintainers must understand the
	changes made to current versions of the kernel, and show these changes
	fit into older versions in order to make the necessary merges and
	modifications to the older versions. Current tools provide information
	about repositories through the directed acyclic graph (DAG) which is
	helpful for smaller projects, but with the scale and number of branches
	in the kernel, the DAG becomes overwhelming very quickly.

@@

German et al. recorded the metadata of every commit and merge in the Linux git
repository from 2012 to 2015, including data that is not stored by git. We are
able to use this information to generate sets of trees rather than a DAG. The
root node of each tree is the top-level merge performed by Linus, which merges
a given commit into the kernel.

In this paper, we present the design decisions behind a web-based tool that
demonstrates the advantages of using the tree model over the use of a DAG. Our
tool provides information about the location of a given commit in the
respective merge tree, the files edited in the commit or merge, the modules
edited in the commit or merge, and the commit message of a given commit or
merge. The tool allows users various filters, including the release, a keyword
or phrase from a log, the name of the author, or the commit id. The user can
request all the top-level merges containing a commit or merge that matches the
query, or all commits and merges that match the query.

@@

Gitk, Gitg, and other similar git repository visualizing tools display the DAG.
For smaller projects, this model is able to provide meaningful information, but
in large projects like the Linux kernel, the branches become too tangled and
deep to derive any meaning from the DAG.

@@

\evantodo{Picture of gitk DAG and github failing}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/empty.png}
	\caption{}
	\label{}
\end{figure}

University of Maryland presented a treemap design for displaying all the files
in a given release. This information doesn't provide meaining about what has
changed. The information within the treemap does not provide clear insight on
the meaning of the files, what changes were made, or even the size. The treemap
structure provides information on where in the directory tree the file exists.

@@

\evantodo{Picture of visualization}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/empty.png}
	\caption{}
	\label{}
\end{figure}

Moghaddam designed a graph showing how various commits in the Kernel were
linked together. This graph doesn't provide a clear picture of what is
happening though, and gives no insight to the hierarchy of the data. It
provides information about who authored the commit, and when the commit was
authored.
%% http://web.uvic.ca/~arasbm/gitVisualizations/linuxRGraph.html
%% Find paper for this maybe?

\evantodo{Picture of graph}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/empty.png}
	\caption{}
	\label{}
\end{figure}

@@

\evantodo{Make a vine diagram}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/empty.png}
	\caption{}
	\label{}
\end{figure}

@@

\evantodo{Picture of tree}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/empty.png}
	\caption{}
	\label{}
\end{figure}

@@

\evantodo{Picture of list tree}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/empty.png}
	\caption{}
	\label{}
\end{figure}

@@

\evantodo{Picture of breadcrumbs}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/empty.png}
	\caption{}
	\label{}
\end{figure}

@@

\evantodo{Picture of files}
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/empty.png}
	\caption{}
	\label{}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/empty.png}
	\caption{}
	\label{fig:AndrewMortonMerges}
\end{figure}

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/empty.png}
	\caption{}
	\label{fig:AndrewMorton}
\end{figure}

>>>>

	With an average of over 900 top-level merges into the Linux kernel per
	release, some containing thousands of commits, many containing hundreds
	of commits, maintenance of older versions of the kernel becomes nearly
	impossible. For security, performance, and changing hardware,
	maintainers must understand the changes made to current versions of the
	kernel, and show these changes fit into older versions in order to make
	the necessary merges and modifications to the older versions. Current
	tools provide information about repositories through the directed
	acyclic graph (DAG) which is helpful for smaller projects, but with the
	scale and number of branches in the kernel, the DAG becomes
	overwhelming very quickly.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.47\textwidth]{figures/gitk.png}
	\caption{DAG view in Gitk}
	\label{fig:gitk}
\end{figure}

The second issue with performing searches is that git log, gitk, and other
tools only store the authored date of a commit. A commit may be merged at any
time, regardless of when the commit was authored. Because of this, performing
date-range queries does not provide meaningful results. Performing a date-range
query using other tools over the span of a release will contain results that
are for previous versions of the kernel, and may not contain all of the results
for that kernel if patches were merged after the release date.

German et al. recorded the metadata of every commit and merge in the Linux git
repository from 2012 to 2015, including data that is not stored by git. We are
able to use this information to generate sets of trees instead of a DAG. The
root node of each tree is the top-level merge performed by Linus, which merges
a given commit into the kernel.

In this paper, we present the design decisions behind a web-based tool,
demonstrating the advantages of our tree model over the use of a DAG. Our tool
provides information about the location of a given commit in the respective
merge tree, the files edited, the modules edited, and the commit message in a
given commit or merge. The tool allows users to apply various filters, including
the release, a keyword or phrase from the log preview, the name of the author,
or the commit id. The user can request all the top-level merges containing a
commit or merge that matches the query, or all commits and merges that match
the query.

Our model of the tool provides many advantages other tools. Breaking the data
by merge tree removes the commits and merges to other components of the kernel
from the visualization, providing a clearer picture of what is happening in a
given merge.

No top-level merges are merged to an earlier version of the kernel after the
release date. Because of our tree construction, we are able to use these
top-level merges to find all merges effecting a version of the kernel,
regardless of when they were authored and merged. This provides us with
mechanisms for performing date-range queries that are able to provide
meaningful information.

@@

\subsection{Gitk}
Gitk, Gitg, and other similar git repository visualizing tools use the DAG as
the central organization. For smaller projects, this model is sufficient for
providing meaningful information, but in larger projects like the Linux kernel,
the branches become too tangled and too deep to derive any meaning from the
DAG. The DAG model allows users to go to the next commit in the chain, go to
the previous commit in the chain, or jump to the parent merge. This suggest
that gitk and similar tools are designed for users working with a bottom-to-top
approach. With this model, it is difficult for users to see what other commits
are involved with a given merge. Gitk only provides file information on
commits, as it is unable to quickly find all files edited by a merge. It is up
to the user to remember what files were edited in each of the commits involved
in a given merge. For some of the large merges in the Kernel, this is an
impossible task. \evantodo{Find a large one and report how many files are
there} Other DAG visualization systems, like the GitHub viewer, are unable to
provide a visualization for projects that are as large as the
kernel.\evantodo{Show picture of github failing}

@@

% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

\subsection{Treemap visualizer}
University of Maryland presented a treemap design for displaying all the files
in a given release. This information doesn't provide meaining about what has
changed. The information within the treemap does not provide clear insight on
the meaning of the files, what changes were made, or even the size. The treemap
structure provides information on where in the directory tree the file exists.

@@

\evantodo{Picture of visualization}
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

\subsection{List viewer}
Moghaddam designed a graph showing how various commits in the Kernel were
linked together. This graph doesn't provide a clear picture of what is
happening though, and gives no insight to the hierarchy of the data. It
provides information about who authored the commit, and when the commit was
authored.
%% http://web.uvic.ca/~arasbm/gitVisualizations/linuxRGraph.html
%% Find paper for this maybe?

\evantodo{Picture of graph}
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

@@

\evantodo{Make a vine diagram}
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

@@

\evantodo{Picture of tree}
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

@@

\evantodo{Picture of list tree}
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

@@

\evantodo{Picture of breadcrumbs}
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

@@

\evantodo{Picture of files}
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{}
% \end{figure}

@@

% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{fig:AndrewMortonMerges}
% \end{figure}
%
% \begin{figure}[h!]
% 	\centering
% 	\includegraphics[width=0.47\textwidth]{figures/empty.png}
% 	\caption{}
% 	\label{fig:AndrewMorton}
% \end{figure}
